A meta-analysis of fungicide effects on mungbean powdery mildew

### 2021-06-02 03_Yield_MetaAnalysis.Rmd
cache stability chunk and change plot line thickness

To check the stability in the network analysis we will rerun the chosen model 15 times. 
Each run, one of the 15 trials will be excluded from the analysis to detect if any estimates varied significantly indicating an unstable network meta-analysis.
```{r stability}
stab_PM_mv <- 
   lapply(unique(PM_dat_Y$trial_ref), function(Trial){

@@

stab_df %>%
   ggplot(aes(Tnum, estimates, colour = treat))+
   geom_line()

stab_df %>%
   ggplot(aes(Tnum, p, colour = treat))+
   geom_line()+
   scale_y_log10()

stab_df %>%
   group_by(treat) %>%
   summarise(minEst = min(estimates),
             medEst = median(estimates),
             maxEst = max(estimates),
             minP = min(p),
             medP = median(p),
             maxP= max(p))
```

>>>>

To check the stability in the network analysis we will rerun the chosen model 15 times. 
Each run, one of the 15 trials will be excluded from the analysis to detect if any estimates varied significantly indicating an unstable network meta-analysis.
```{r stability, cache=TRUE}
stab_PM_mv <- 
   lapply(unique(PM_dat_Y$trial_ref), function(Trial){

@@

stab_df %>%
   ggplot(aes(Tnum, estimates, colour = treat))+
   geom_line(size = 1)

stab_df %>%
   ggplot(aes(Tnum, p, colour = treat))+
   geom_line(size = 1)+
   scale_y_log10()

stab_df %>%
   group_by(treat) %>%
   summarise(minEst = min(estimates),
             medEst = median(estimates),
             maxEst = max(estimates),
             minP = min(p),
             medP = median(p),
             maxP= max(p))
stab_df[Tnum == 9]
```
